### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@0de5f26cf496d1a6a2c7f84605472734d9ca3027 🚀

\begin{longtable}[]{@{}lll@{}}
\toprule
Method & Embedded object & Reference\tabularnewline
\midrule
\endhead
DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
\bottomrule
\end{longtable}

@@

>>>>

\begin{longtable}[]{@{}lll@{}}
\toprule
Method & Embedded object & Reference\tabularnewline
\midrule
\endhead
DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
graph2vec & sub-graph embedding & Narayanan et al. (2017)\tabularnewline
\bottomrule
\end{longtable}

@@

\leavevmode\hypertarget{ref-Narayanan2017GraLea}{}%
Narayanan, A., Chandramohan, M., Venkatesan, R., Chen, L., Liu, Y., \&
Jaiswal, S. (2017, July 17). \emph{Graph2vec: Learning Distributed
Representations of Graphs}. \url{http://arxiv.org/abs/1707.05005}
